Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-07-02 main_revision.tex

The impact of \emph{slatop} on fertilization was different at every site. For MET, \emph{slatop} was the most important control over N responses, with cheaper leaves allowing a greater LAI/GPP feedback in response to the N fertilization. At NWR, the opposite behaviour was found, with high SLA reducing the impact of N in cases where the pre-fertilization LAI meant that a saturating response of GPP was found.

>>>>

The impact of \emph{slatop} on fertilization was different at every site. For MET, \emph{slatop} was the most important control over N responses, with higher values allowing a greater LAI/GPP feedback in response to the N fertilization. At NWR, the opposite behaviour was found, with high SLA reducing the impact of N in cases where the pre-fertilization LAI meant that a saturating response of GPP was found. At HVF, higher values of \emph{slatop} slightly reduced both CO$_{2}$ and N fertilization for the same reason (although the range of variation at HVF is only 5\% between the highest and lowest values, as opposed to 40\% at NWR).
